\LARGE \bf Longitudinal Trajectory Planning and Tracking for Fixed-Path Autonomous Driving

### 2016-01-13 paper1.tex
removed urls in citations fleshed out the segmentation section added two figures to segmentation section changing notation (WIP)

\usepackage[pdftex]{graphicx}
% \usepackage[hypcap]{caption}
\usepackage[noadjust]{cite}

@@

Consider, as a starting point, the case in which a vehicle is at rest and needs to accelerate to some travelling speed, maintain that speed for some distance, then brake to a stop at a prescribed end location.
Figure \ref{fig:7phaseprofile} shows this trajectory over time.
The problem is defined by the vector of known values $\bar{G}  = [v_i, v_f, L, v_m]$, being initial speed, final speed, the total distance, and the speed limit, respectively.
If the desired peak acceleration and jerk ($a_m$ and $j_m$, respectively) are known, then the profile with $M$ jerk phases (7 in this case) can be generated by solving for the time intervals $[\Delta t_1, ..., \Delta t_M]$.
Jerk and peak acceleration may be different when reducing speed versus increasing speed to more closely mirror human driving behavior \emph{Citation}.
The user-defined parameters now become $\bar{a}_m = [a^+_m , a^-_m]$ and $\bar{j}_m = [j^+_m , j^-_m]$.
There are, however, multiple solutions for $\Delta t_2$, $\Delta t_4$, and $\Delta t_6$.
The proper solution must be chosen by eliminating negative and complex solutions.

It is obvious that there are many cases in which this solution will fail.
For instance, if $L$ is sufficiently short and $v_m$ is sufficiently high, then it will not be possible to ever reach $v_m$ with realistic values of $\bar{a}_m$ and $\bar{j}_m$.
The authors then propose that 4 other basic profiles be defined, and an algorithm constructed which judiciously chooses the appropriate profile for every segment defined by a vector $\bf{G}$.
The other profiles are explained below in section \ref{sec:jerkprofiles}.
A path is then a set of $N_s$ segments, each of which is defined by a set of parameters $G_k, k = 1 ... N_s$ and can be solved indivually in sequence.
Determination of where to break a path into segments is discussed below in Section \ref{sec:pathsegmentation}.

There are a total of five potential jerk profiles which have been created to cover all feasible values in $\bar{G}$. All impossible scenarios are automatically ruled out.

@@

In the case mentioned above, wherein the speed limit is too high for a solution to exist for a 7 phase profile, The middle travel period is removed, so that the vehicle increases speed and then immediately decreases speed. 
The peak speed in this case has a solution, but cannot be manipulated directly.

@@

To decide which profile to employ, a cascade approach is used. Analytic values of time intervals are evaluated for each profile by plugging in values of $\bar{G}$, $\bar{a}_m$, and $\bar{j}_m$ until all time intervals are positive and real. 
The order in which they are attempted is: 7 $\rightarrow$ 6 $\rightarrow$ 4 $\rightarrow$ 4R $\rightarrow$ 3.

@@

% make sure to incorporate extensibility to other constraints
The goal of the segmentation process is to divide a given path into multiple portions where each has a uniform upper limit on speed, acceleration, and braking.
After this is done, the process described above in Section \ref{sec:jerkprofiles} may be applied to each of the segments.

To begin, 5 values must be computed for each point in the planned path consisting of $N_p$ points: $v_{m,k}$, $a^+_{m,k}$, $a^-_{m,k}$, $j^+_{m,k}$, and $j^-_{m,k}$ for $k = 1, ... N_p$ . Each value is a minimax, i.e., a minimum of several maxima computed from various constraints. For instance, ...

For the purposes of this work, two constraints are used for $v_m$: legal speed limit (set constant for the whole path) and lateral acceleration limit. Lateral acceleration constraints are translated into longitudinal speed constraints using the approximation $v_{m,k}(a_{B,y}) = \sqrt{a_{B,y}^{max}/\kappa_k}$ for $k = 1, ..., N_p$. For each path point, the value $v_{m,k}(a_{B,y})$ denotes the speed necessary to obtain the limit lateral acceleration, denoted by $a^{max}_{B,y}$. The value $\kappa_k$ denotes the path curvature at each point. For the sake of simplicity, the values of $a^+_{m,k}$, $a^-_{m,k}$, $j^+_{m,k}$, and $j^-_{m,k}$ are all set constant for the entire path, using recommendations from ~\cite{Maurya2012}
An arbitrary set of constraints may

>>>>

\usepackage[pdftex]{graphicx}
% \usepackage
\usepackage[noadjust]{cite}

@@

Consider, as a starting point, the case in which a vehicle is at rest and needs to accelerate to some travelling speed, maintain that speed for some distance, then brake to a stop at a prescribed end location.
Figure \ref{fig:7phaseprofile} shows this trajectory over time.
The problem is defined by the vector of known values $\bf{b}  = [v_i, a_i, L, v_m, v_f]$, being initial speed, initial acceleration, the total distance, speed limit, and the final speed, respectively.
If the magnitude of the desired peak acceleration and jerk ($a_m$ and $j_m$, respectively) are known, then the profile with $M$ jerk phases (7 in this case) can be generated by solving for the time intervals $[\Delta t_1, ..., \Delta t_M]$.
Jerk and peak acceleration may be different when reducing speed versus increasing speed to more closely mirror human driving behavior \emph{Citation}.
The remaining parameters yet to be set now become $\bf{a}_m = [a^+_m , a^-_m]$ and $\bf{j}_m = [j^+_m , j^-_m]$.
There are, however, multiple solutions for $\Delta t_2$, $\Delta t_4$, and $\Delta t_6$.
The proper solution must be chosen by eliminating negative and complex solutions.

It is obvious that there are many cases in which this solution will fail.
For instance, if $L$ is sufficiently short and $v_m$ is sufficiently high, then it will not be possible to ever reach $v_m$ with realistic values of $\bf{a}_m$ and $\bf{j}_m$.
The authors then propose that 4 other basic profiles be defined, and an algorithm constructed which judiciously chooses the appropriate profile for every segment defined by a vector $\bf{b}$.
The other profiles are explained below in section \ref{sec:jerkprofiles}.
A path is then a set of $N_s$ segments, each of which is defined by a set of parameters $\bf{b}_k, k = 1 ... N_s$ and can be solved indivually in sequence.
Determination of where to break a path into segments is discussed below in Section \ref{sec:pathsegmentation}.

There are a total of five potential jerk profiles which have been created to cover all feasible values in $\bf{b}$. All impossible scenarios are automatically ruled out.

@@

In the case mentioned above, the speed limit is too high for a solution to exist for a 7 phase profile.
The middle travel period is removed, so that the vehicle increases speed and then immediately decreases speed. 
The peak speed in this case has a solution, but cannot be manipulated directly.

@@

To decide which profile to employ, a cascade approach is used.
Analytic values of time intervals are evaluated for each profile by plugging in values of $\bf{b}$, $\bf{a}_m$, and $\bf{j}_m$ until all time intervals are positive and real. 
The order in which they are attempted is: 7 $\rightarrow$ 6 $\rightarrow$ 4 $\rightarrow$ 4R $\rightarrow$ 3.

@@

% make sure to incorporate extensibility to other constraints
The goal of the segmentation process is to divide a given path into multiple portions where each has a uniform upper limit on speed, acceleration, and braking.
There are 3 steps in the segmentation process:
\begin{enumerate}
  \item \emph{Ceiling calculation}, where $\bf{b}$, $\bf{a}_m$, and $\bf{j}_m$ are found for every point in the given path.
  \item \emph{Clustering}, in which path points are grouped sequentially.
  \item \emph{Consolidation}, in which a single $\bf{b}$, $\bf{a}_m$, and $\bf{j}_m$ is selected for each segment.
\end{enumerate}
After this is done, the process described above in Section \ref{sec:jerkprofiles} may be applied to each of the segments.

The ceiling calculation is a minimax problem.
Each of the 9 scalars is a minimum of several maxima computed from an arbitrary set of constraints.
For instance, ... \emph{put examples of things we didn't do...}
% How we actually did this.
For the purposes of developing a simple example application, two constraints will be used for $v_{m,k}$: legal speed limit ( $SL$, set constant for the whole path) and lateral acceleration limit ($a_{B,y}^{max}$. 
Lateral acceleration constraints are translated into longitudinal speed constraints using the approximation $v_{m,k}(a_{B,y}) = \sqrt{a_{B,y}^{max}/\kappa_k}$ for $k = 1, ..., N_p$.
For each path point, the value $v_{m,k}(a_{B,y}^{max})$ denotes the speed necessary to obtain the limit lateral acceleration, denoted by $a^{max}_{B,y}$.
The value $\kappa_k$ denotes the path curvature at each point.
For the sake of simplicity, the values of $a^+_{m,k}$, $a^-_{m,k}$, $j^+_{m,k}$, and $j^-_{m,k}$ are all set constant for the entire path, using values from \cite{Maurya2012,Hoberock1977,Long2000}.

This information is used to choose the segment boundaries in the clustering step.
Any number of clustering algorithms may be used here, and prudent choice of segment boundaries is arguably one of the most critical pieces of trajectory planning process.
For the present example, we will choose a simple univariate heuristic which essentially identifies curves in the roadway.
Each time that $v_{m,k} < SL$ becomes true, a curve is beginning, and a segment boundary is drawn.
Each time that $v_{m,k} = SL$ is once again true, the current curve has ended, and another segment boundary is drawn.
Figure~\ref{fig:course_highlight_turns} shows the result of this algorithm.

\begin{figure}[thpb]
  \label{fig:course_highlight_turns}
  \centering
  \includegraphics[width=\columnwidth]{graphics/course_highlighted_turns.png}
  \caption{Clustering output for a short path when using an algorithm which draws segment boundaries around curves.}
\end{figure}

In the consolidation step, ...

\begin{figure}[thpb]
  \label{fig:consolidation_speed_ceiling}
  \centering
  \includegraphics[width=\columnwidth]{graphics/speed_ceiling.png}
\end{figure}

The power of this algorithm is that any set and number of constraints may be used ... \emph{etc., etc., ...}
